---
title: "PrepareData"
author: "Jean-Francois Chartier"
date: "4 février 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#install packages
```{r}

if ("stringr" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(stringr)

if ("magrittr" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(magrittr)


```

#Load data
```{r}
load("df_training_set.rda")
load("df_test_set.rda")

load("df_training_set_2.rda")

df_training_set=rbind(df_training_set, df_training_set_2)
id.doc <- unique(df_training_set_2$ID_final)
#id.doc=unique(str_trim(id.doc, "both"))
id.doc=as.factor(id.doc)
#df_test_set$ID_final=str_trim(df_test_set$ID_final, "both") %>%as.factor(.)

df_test_set.new = df_test_set[!(df_test_set$ID_final %in% id.doc),]
#check 
is.present=sapply(id.doc, function(x){
  x%in%df_test_set$ID_final
})


```

#save useful data only
```{r}
mood.industry.data=data.frame(ID_final=df_training_set$ID_final, text=df_training_set$seltext, sponsor.feature=df_training_set$SPONSOR2, type.feature=df_training_set$TYPE, act.feature=df_training_set$ACT, label_of_class=df_training_set$codename, training.set=rep(T,length(df_training_set$seltext)))

mood.industry.data=rbind(mood.industry.data, data.frame(ID_final=df_test_set.new$ID_final, text=df_test_set.new$group_sentences, sponsor.feature=df_test_set.new$SPONSOR2, type.feature=df_test_set.new$TYPE, act.feature=df_test_set.new$ACT, label_of_class= rep(NA,length(df_test_set.new$group_sentences)), training.set= rep(F,length(df_test_set.new$group_sentences))))

#trim data
mood.industry.data$text=str_trim(mood.industry.data$text)

#correct error in class label
mood.industry.data$label_of_class[mood.industry.data$label_of_class=="statment_professional"]="statement_professional"
mood.industry.data$label_of_class=droplevels(mood.industry.data$label_of_class)

saveRDS(mood.industry.data, "mood.industry.data.rds")
```


Get new dataframe from 2019-02-19
#save useful data only
```{r}
load("df_exemplars_2019-02-19.rda")

mood.industry.data=data.frame(ID_final=df$ID_final, text=df$group_sentences, sponsor.feature=df$SPONSOR2, type.feature=df$TYPE, act.feature=df$ACT, label_of_class=df$codename, text.all.rias=df$RIAS_clean, stringsAsFactors = F)

training.set=sapply(mood.industry.data$label_of_class, FUN = function(x){
  ifelse(test = is.na(x), FALSE, TRUE)
})
mood.industry.data$training.set=training.set
#trim data
mood.industry.data$text=str_trim(mood.industry.data$text)

#combine class labels
statement_institution=(mood.industry.data$label_of_class=="statement_firstnations" | mood.industry.data$label_of_class=="statement_expert" |  mood.industry.data$label_of_class=="statement_institution")
mood.industry.data$label_of_class[statement_institution]="statement_institution"

statement_advocacy=(mood.industry.data$label_of_class=="statement_advocacy" | mood.industry.data$label_of_class=="statement_professional")
mood.industry.data$label_of_class[statement_advocacy]="statement_advocacy"

saveRDS(mood.industry.data, "mood.industry.data.rds")
```

#Add 3th annotations
##Read data.frame mood.industry.data.rds
```{r}
mood.industry.data=readRDS("mood.industry.data.rds")

new.annotation=read.csv(file = "hierar_lr2.csv", header = T, strip.white = T, blank.lines.skip = T, stringsAsFactors = F, encoding = "UTF-8")
```

##update class label
from older annotation
```{r}
negative.class=(mood.industry.data$label_of_class=="no_comment" | mood.industry.data$label_of_class=="no_consultation" |  mood.industry.data$label_of_class=="no_statement")

mood.industry.data$new.class.label=mood.industry.data$label_of_class

mood.industry.data$new.class.label[negative.class==T]="is.not.consultation.label"
```

##encode annotation as probability
```{r}
#id.new.annotation=(apply(new.annotation[, 16:18], MARGIN = 1, function(x) {is.nx==c(NA,NA,NA)}))

#id.new.annotation=rowSums(new.annotation[, 16:18]) %>%is.na(.)%>%magrittr::equals(F) %>% which()

#id.new.isNotConsultation=new.annotation[, 16:18] %>% rowSums(.) %>%equals(0) %>%which()

#id.new.2multi.label=new.annotation[, 16:18] %>% rowSums(.) %>%equals(2) %>%which()

#id.new.3multi.label=new.annotation[, 16:18] %>% rowSums(.) %>%equals(3) %>%which()

new.annotation.sum=new.annotation[, 16:18] %>% rowSums(.)

new.annotation.prob=new.annotation[, 16:18] %>%divide_by(new.annotation.sum)%>%set_colnames(c(paste0(colnames(new.annotation[,16:18]), ".prob")))

#add is.not.consultation.label prob value

is.not.consultation.prob=sapply(new.annotation.sum, function(x){
  if (is.na(x)){
    NA
  } else if (x==0){
    1
  }
  else {
    0
  }
})
new.annotation.prob$is.not.consultation.prob=is.not.consultation.prob

#id.duplicate = which(duplicated(new.annotation[id.new.multi.label,c(3)]))

#unique.new.annotation=unique(new.annotation)

#head(new.annotation[is.na(new.annotation$)])

```

##get old annotation prob
```{r}
idTain=which(mood.industry.data$training.set==T)
#id.duplicate = which(duplicated(mood.industry.data[idTain,c(2)]))
#id.duplicate = which(stringi::stri_duplicated(as.character(mood.industry.data[idTain,c(2)])))
#id.duplicate = which(duplicated(as.character(mood.industry.data[idTain,c(2)])))

#finding frequency of duplicated element
#https://stackoverflow.com/questions/18201074/find-how-many-times-duplicated-rows-repeat-in-r-data-frame
#freq.of.dupli=group_size(dplyr::group_by(mood.industry.data[idTain,c(2)]))

#freq.of.dupli=mood.industry.data[idTain,c(2:4)] %>% dplyr::group_by(text, sponsor.feature, type.feature) %>% dplyr::group_size()%>%rep(.,.)

freq.of.dupli=(mood.industry.data[idTain,c(2:4)])%>%plyr::count(., vars = c("text", "sponsor.feature", "type.feature"))


freq.of.dupli.by.obs=apply(mood.industry.data[idTain,c(2:4)], MARGIN = 1, function(x){
  #str(x)
  i=apply(freq.of.dupli[,1:3], MARGIN = 1, function(y){
    all(x==y)
  })
  #i=prodlim::row.match(x = x, table = freq.of.dupli[,1:3])
  #print(i)
  freq.of.dupli$freq[i] %>%data.table::first()
})

#View(cbind(mood.industry.data[idTain,c(2:4,9)], freq.of.dupli.by.obs))

#get number of different annotations for same exemplar
n.anno.for.dupli.obs=apply(mood.industry.data[idTain,c(2:4)], MARGIN = 1, function(x){
  #str(x)
  i=apply(mood.industry.data[idTain,c(2:4)], MARGIN = 1, function(y){
    all(x==y)
  })
  #i=prodlim::row.match(x = x, table = freq.of.dupli[,1:3])
  #print(i)
  mood.industry.data$new.class.label[idTain][i]%>%unique(.)%>%length(.)
  #freq.of.dupli$freq[i] %>%data.table::first()
})

View(cbind(mood.industry.data[idTain,c(2:4,9)], freq.of.dupli.by.obs, n.anno.for.dupli.obs))

old.annotation.prob=1/n.anno.for.dupli.obs

```

##get old annotation prob
```{r}
annotations.prob.labels=mood.industry.data$new.class.label[idTain]%>%unique(.) #%>%paste0(., "_prob")

anno.prob.for.obs=apply(mood.industry.data[idTain,c(2:4)], MARGIN = 1, function(x){
  #str(x)
  i=apply(mood.industry.data[idTain,c(2:4)], MARGIN = 1, function(y){
    all(x==y)
  })
  #print(i)
  
  pr.of.label=rep(0, length(annotations.prob.labels)) %>%set_names(annotations.prob.labels)
  
  #get how many different labels used
  labels=mood.industry.data$new.class.label[idTain][i]%>%unique(.)
  p=1/length(labels)
  #print(p)
  
  for (j in 1: length(labels))
  {
    pr.of.label[names(pr.of.label)==labels[j]]=p
  }
  
  #sapply(labels, function(l){
    #print(equals(names(pr.of.label),l))
    #pr.of.label[equals(names(pr.of.label),l)]=p
  #})
  #print(pr.of.label)
  pr.of.label
  #data.frame(annotations.prob.labels)
  #freq.of.dupli$freq[i] %>%data.table::first()
})%>%t(.)

anno.prob.for.obs=anno.prob.for.obs%>%set_colnames(.,paste0(colnames(anno.prob.for.obs), "_prob"))%>%as.data.frame()
```


##assign new annotation
```{r}

all.new.annotation.prob = data.frame(is.not.consultation.prob=numeric(length=nrow(mood.industry.data)), statement.advocacy.prob=numeric(length=nrow(mood.industry.data)), statement.institution.prob=numeric(length=nrow(mood.industry.data)), statement.industry.prob=numeric(length=nrow(mood.industry.data)))

#adding old annotation prob
all.new.annotation.prob$is.not.consultation.prob[idTain]=anno.prob.for.obs$is.not.consultation.label_prob
all.new.annotation.prob$statement.advocacy.prob[idTain]=anno.prob.for.obs$statement_advocacy_prob
all.new.annotation.prob$statement.industry.prob[idTain]=anno.prob.for.obs$statement_industry_prob
all.new.annotation.prob$statement.institution.prob[idTain]=anno.prob.for.obs$statement_institution_prob

#adding new annotation prob
all.new.annotation.prob$is.not.consultation.prob[-idTain]=new.annotation.prob$is.not.consultation.prob
all.new.annotation.prob$statement.advocacy.prob[-idTain]=new.annotation.prob$statement_advocacy_2.prob
all.new.annotation.prob$statement.industry.prob[-idTain]=new.annotation.prob$statement_industry_2.prob
all.new.annotation.prob$statement.institution.prob[-idTain]=new.annotation.prob$statement_institution_2.prob

#combine dataframes 
mood.industry.data=cbind(mood.industry.data, all.new.annotation.prob)

#update idTrain
newIdTrain=new.annotation.prob$is.not.consultation.prob %>% is.na(.)==F
mood.industry.data$training.set[-idTain]=newIdTrain

#add unique id
mood.industry.data$uniqueID=1:nrow(mood.industry.data)
```

##post correction for NaN
some sample use NaN instead of NA. Replace all NaN in idTrain by 0.0
```{r}
mood.industry.data[mood.industry.data$training.set==T, 11:13] = apply(mood.industry.data[mood.industry.data$training.set==T, 11:13], 1, function(x){
  #print(x)
  
  x=if(all(x=="NaN")){
    print(x)
    y=c(0.0,0.0,0.0)
  } else{
    y=x
  }
  y
  #print(x)
})%>%t(.)
```


```{r}
saveRDS(mood.industry.data, "mood.industry.data.with.prob.rds")
```

