---
title: "RegressionAnalysisOfAnnotationProb"
author: "Jean-Francois Chartier"
date: "22 mars 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#install packages
```{r}

if ("magrittr" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(magrittr)

if ("caret" %in% installed.packages()==FALSE){
  install.packages('caret',dependencies = TRUE)
}
library(caret)
if ("rpart" %in% installed.packages()==FALSE){
  install.packages('rpart',dependencies = TRUE)
}
library(rpart)

if ("quanteda" %in% installed.packages()==FALSE){
  install.packages('quanteda',dependencies = TRUE)
}
library(quanteda)

```


```{r}
#function to create a unit normed vector
normVector <- function(x) 
{
  if(sum(x)==0)
    return (x)
  else 
    return (x / sqrt(sum(x^2)))
  
}
#function to norm many vectors
normRowVectors<-function(m){
  t(apply(m, MARGIN = 1, FUN = function(x) normVector(x)))
}
```


#read data
```{r}
mood.industry.data=readRDS("mood.industry.data.with.prob.rds")
wordfrequency.matrix.regcan=readRDS("wordfrequency.matrix.regcan.rds")
#reduced.svd.regcan.doc=readRDS("reduced.svd.regcan.doc.rds")

#svd.of.regcan.from.irba = readRDS("svd.of.regcan.from.irba.150.rds")

#reduced.svd.regcan.doc=  as.matrix(svd.of.regcan.from.irba$u %*% solve(diag((svd.of.regcan.from.irba$d)))) #%>% normRowVectors()
#colnames(reduced.svd.regcan.doc)=svd.of.regcan.from.irba$feature.names

ngramfrequency.matrix.regcan=readRDS("ngramfrequency.matrix.regcan.rds")

reduced.matrix.context.rias=readRDS("reduced.matrix.context.rias.rds")

sentiment.regcan.matrix=readRDS("sentiment.regcan.matrix.rds")
```

#read all latent models
```{r}
n.latents=c(50, 100, 150, 200, 300, 400, 500, 800)

latent.models=lapply(n.latents, FUN = function(k){
  svd.of.regcan.from.irba = readRDS(paste0("svd.of.regcan.from.irba.", k, ".rds"))
  
  reduced.svd.regcan.doc=  as.matrix(svd.of.regcan.from.irba$u %*% solve(diag((svd.of.regcan.from.irba$d)))) #%>% normRowVectors()
  colnames(reduced.svd.regcan.doc)=paste0(k,".",svd.of.regcan.from.irba$feature.names)
  reduced.svd.regcan.doc
  })

```


#get training id
```{r}

id.train=mood.industry.data$training.set==T
```

#Combine features
##add meta data
```{r}
data.classification=mood.industry.data[,c(3:5,8, 10:13)]
```

##add word-matrix frequency
```{r}
data.classification=cbind(data.classification, as.matrix(wordfrequency.matrix.regcan)%>%set_colnames(., wordfrequency.matrix.regcan@Dimnames$features))
```

##add n-gram
```{r}
data.classification=cbind(data.classification, as.matrix(ngramfrequency.matrix.regcan)%>%set_colnames(., ngramfrequency.matrix.regcan@Dimnames$features))
```

##add sentiment features
```{r}
data.classification=cbind(data.classification, sentiment.regcan.matrix)
```

##add all latent models
```{r}
all.latent.models=do.call("cbind", latent.models)
data.classification=cbind(data.classification, all.latent.models)
```

##add global.rias.latent
```{r}
#add global.rias.latent
data.classification=cbind(data.classification, reduced.matrix.context.rias)

```

#prepare data for ml
```{r}

#change NA in sponsor
#data.classification=data.classification.train
i=data.classification$sponsor.feature%>%is.na(.)
data.classification$sponsor.feature=as.character(data.classification$sponsor.feature)
data.classification$sponsor.feature[i]="unknown.sponsor"
data.classification$sponsor.feature=as.factor(data.classification$sponsor.feature)

#extract train and test sets
data.classification.train=data.classification[id.train, ]
data.classification.test=data.classification[id.train==F, ]

```

#Regression Prediction Analysis
##is.not.consultation annotation 
```{r}
#subset of id train
seed=123
id.sub.train <- sample(nrow(data.classification.train), 2/3 * nrow(data.classification.train))
```

###train on sub training set
```{r}
data.classification.train.not.consultation = data.classification.train[,-c(4,6:8)]

rf.bin.model=ranger::ranger(dependent.variable.name = "is.not.consultation.prob", data=data.classification.train.not.consultation[id.sub.train,], num.trees=20000, num.threads=6, classification=F, importance = "impurity")

View(rf.bin.model$variable.importance, title = "impurity over is.not.consultation")

```

###Predict regression on 1/3 of training set
```{r}
rf.bin.pred=predict(rf.bin.model, data = data.classification.train.not.consultation[-id.sub.train,])

observed=data.classification.train.not.consultation$is.not.consultation.prob[-id.sub.train]
predicted=rf.bin.pred$predictions

cor=cor(observed, predicted)
rmse=RMSE(observed, predicted)
evaluations=data.frame(class="is.not.consultation", correlation=cor, rmse=rmse)

axisRange <- extendrange(c(observed, predicted))
plot(observed, predicted, xlab = "observations", ylab = "predictions", main = "Observations and predictions for no statement likelihood")
abline(a = 0, b = 1,  col  = "darkgrey", lty = 2)

```

##institution annotation 
###train on sub training set
```{r}

data.classification.train.institution = data.classification.train[,-c(4:6,8)]

rf.institution.model=ranger::ranger(dependent.variable.name = "statement.institution.prob", data=data.classification.train.institution[id.sub.train,], num.trees=20000, num.threads=6, classification=F, importance = "impurity")

View(rf.institution.model$variable.importance, title = "impurity over statement.institution.prob")

```

###Predict regression on 1/3 of training set
```{r}
rf.institution.pred=predict(rf.institution.model, data = data.classification.train.institution[-id.sub.train,])

observed=data.classification.train.institution$statement.institution.prob[-id.sub.train]
predicted=rf.institution.pred$predictions

cor=cor(observed, predicted)
rmse=RMSE(observed, predicted)
evaluations=rbind(evaluations, data.frame(class="institution", correlation=cor, rmse=rmse))

axisRange <- extendrange(c(observed, predicted))
plot(observed, predicted, xlab = "observations", ylab = "predictions", main = "Observations and predictions for institution statement likelihood")
abline(a = 0, b = 1,  col  = "darkgrey", lty = 2)

```

##advocacy annotation 
###train on sub training set
```{r}

data.classification.train.advocacy = data.classification.train[,-c(4:5,7:8)]

rf.advocacy.model=ranger::ranger(dependent.variable.name = "statement.advocacy.prob", data=data.classification.train.advocacy[id.sub.train,], num.trees=20000, num.threads=6, classification=F, importance = "impurity")

View(rf.advocacy.model$variable.importance, title = "impurity over statement.advocacy.prob")

```

###Predict regression on 1/3 of training set
```{r}
rf.advocacy.pred=predict(rf.advocacy.model, data = data.classification.train.advocacy[-id.sub.train,])

observed=data.classification.train.advocacy$statement.advocacy.prob[-id.sub.train]
predicted=rf.advocacy.pred$predictions

cor=cor(observed, predicted)
rmse=RMSE(observed, predicted)
evaluations=rbind(evaluations, data.frame(class="advocacy", correlation=cor, rmse=rmse))

axisRange <- extendrange(c(observed, predicted))
plot(observed, predicted, xlab = "observations", ylab = "predictions", main = "Observations and predictions for advocacy statement likelihood")
abline(a = 0, b = 1,  col  = "darkgrey", lty = 2)

```
##industry annotation 
###train on sub training set
```{r}

data.classification.train.industry = data.classification.train[,-c(4:7)]

rf.industry.model=ranger::ranger(dependent.variable.name = "statement.industry.prob", data=data.classification.train.industry[id.sub.train,], num.trees=20000, num.threads=6, classification=F, importance = "impurity")

View(rf.industry.model$variable.importance, title = "impurity over statement.industry.prob")

```

###Predict regression on 1/3 of training set
```{r}
rf.industry.pred=predict(rf.industry.model, data = data.classification.train.industry[-id.sub.train,])

observed=data.classification.train.industry$statement.industry.prob[-id.sub.train]
predicted=rf.industry.pred$predictions

cor=cor(observed, predicted)
rmse=RMSE(observed, predicted)
evaluations=rbind(evaluations, data.frame(class="industry", correlation=cor, rmse=rmse))

axisRange <- extendrange(c(observed, predicted))
plot(observed, predicted, xlab = "observations", ylab = "predictions", main = "Observations and predictions for industry statement likelihood")
abline(a = 0, b = 1,  col  = "darkgrey", lty = 2)
```

##Plot Evalutions
```{r}
huxtable::as_huxtable(evaluations,add_colnames=T)%>%huxtable::theme_basic(.)

```



